Automated verification of electrical systems: literature review and case studies of stand-alone solar photovoltaics\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2019-02-05 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We have performed five case studies to evaluate the tools, as described by Table~\ref{tab2}. 
\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3x 325W: in series} & 4x 325W: 2x series and 2x parallel \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4x220Ah: 2x series and 2x parallel\\ autonomy: 48h}} & \makecell{4x 120Ah batteries in series\\ autonomy: 6h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150V/35A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700W with surge of 1,600W} & 1,200W with surge of 1,600W\\
\hline
Power demand & 253W & 263W & 283W & 501W & 915W\\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\end{table}

The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}). Another characteristic of Manaus, based on historical weather data %\cite{Temperature}, 
\cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h. % (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).

@@

Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does the automated verification provide correct results?
\item[RQ2] \textbf{(performance)} How does the  tools compare each other?
\end{enumerate}

It was used two different setups of hardware and different verification engines, combined with different Solvers. The aim was to evaluate different environments and possible user limitation in terms of main processor and RAM memory. All the experiments were performed without a predefined timeout.

@@

Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.

@@

In order to evaluate the verification methods and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool. %Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use. This information was used to know possible flaws from every system in the field.
Experimental setup of HOMER Pro: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.

@@

%
Table~\ref{tab1} summarize the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system. The time expressed at the Table answer the RQ2. Worth to mention that using simulation tool (HOMER Pro) in all case studies, the 1,200W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation. The simulation took less than five seconds to be performed in each case study.

>>>>

We have performed five case studies to evaluate the tools, as described in Table~\ref{tab2}. 
\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3x 325W: in series} & 4x 325W: 2x series and 2x parallel \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4x220Ah: 2x series and 2x parallel\\ autonomy: 48h}} & \makecell{4x 120Ah batteries in series\\ autonomy: 6h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150V/35A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700W with surge of 1,600W} & 1,200W with surge of 1,600W\\
\hline
Power demand & 253W & 263W & 283W & 501W & 915W\\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\end{table}

The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}). Another characteristic of Manaus, based on historical weather data %\cite{Temperature}, 
\cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h. \textcolor{red}{why?} % (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).

@@

Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does the automated verification provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other?
\end{enumerate}

We have used two different setups of hardware and different verification engines, combined with different solvers. The aim was to evaluate different environments and possible user limitation in terms of main processor and RAM memory. All the experiments were performed without a predefined timeout.

@@

Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat \textcolor{red}{which version of minisat?}~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.

@@

In order to evaluate the verification methods and its performance, we have considered five case studies and also compared their performance to the HOMER Pro tool. %Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use. This information was used to know possible flaws from every system in the field.
Experimental setup of HOMER Pro: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.

@@

%
Table~\ref{tab1} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system. The time expressed at the Table answer the RQ2. Worth to mention that using simulation tool (HOMER Pro) in all case studies, the 1,200W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation. The simulation took less than five seconds to be performed in each case study.
